Continuous developmental change explains discontinuities in word learning

### 2019-09-09 journal/ms_full.Rmd
create folder experiment

  None of the authors have any financial interest or a conflict of interest regarding this work and this submission.

@@

figsintext        : no
figurelist        : yes
tablelist         : no
footnotelist      : no
lineno            : yes

@@

In this experiment, we tested participants in the word learning task introduced above (Figure \@ref(fig:task)). More precisely, we explored the predictions related to both distinctiveness and precision. Sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design. Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm [e.g., @frank2016] which allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$. The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}

@@

We report data from $N=$ `r N_good_ch` children ages 4-5 years from a nursery school. An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below). We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk. An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses (again, using preregistered exclusion criteria) because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.

@@

In the exposure trials, participants saw two objects associated with their corresponding sounds. We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound. The second sound-object association followed on the other side of the screen after 500ms. For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).  In the testing trials, participants saw both objects simultaneously and heard only one sound. They completed the trial by selecting which of the two objects corresponded to the sound. The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial.

@@

\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}} \vspace{1em}

>>>>

  'The experiment, sample size, exclusion criteria, and the model’s main predictions were preregistered at https://osf.io/942gv/'

  'All data and analytic code are available at https://github.com/afourtassi/kidswitch'

  'None of the authors have any financial interest or a conflict of interest regarding this work and this submission.'

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

@@

In this experiment, we tested participants in the word learning task introduced above (Figure \@ref(fig:task)). More precisely, we explored the predictions related to both distinctiveness and precision. Sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design. Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is relatively novel for preschoolers, but the tablet paradigm [@frank2016] allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$. The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{https://osf.io/942gv/}

@@

We report data from $N=$ `r N_good_ch` children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below). We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk. An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses (again, using preregistered exclusion criteria) because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.

@@

In the exposure trials, participants saw two objects associated with their corresponding sounds. We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound. The second sound-object association followed on the other side of the screen after 500ms. For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).  In the testing trials, participants saw both objects simultaneously and heard only one sound. They completed the trial by selecting which of the two objects corresponded to the sound. The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}

@@

\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}} \vspace{1em}

# Appendix

We show in Table 2 the output of the regression model we used to analyze behavioral data in the experiment.

### 2019-09-09 journal/ms_full.tex
create folder experiment

\documentclass[english,,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change explains discontinuities in word learning},
            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}

\authornote{

None of the authors have any financial interest or a conflict of
interest regarding this work and this submission.

@@

\begin{figure}[htbp]
\centering
\includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate
responses in the testing phase as a function of stimuli distinctiveness
\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
(For simplicity, we use model 2, which assumes that
\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
\end{figure}

@@

In this experiment, we tested participants in the word learning task
introduced above (Figure \ref{fig:task}). More precisely, we explored
the predictions related to both distinctiveness and precision. Sound
similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were
varied simultaneously in a within-subject design. Two age groups
(preschool children and adults) were tested on the same task\footnote{This
  four-condition within-subject design is relatively novel for
  preschoolers, but we followed the tablet paradigm (e.g., Frank,
  Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to
  gather a relatively large number of trials from each child.} to
explore whether development can be characterized with the uncertainty
parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
exclusion criteria, and the model's main predictions were
pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}

@@

We report data from \(N=\) 63 children ages 4-5 years from a nursery
school. An additional \(N=\) 39 children participated but were removed
from analyses (using preregistered exclusion criteria) because they were
not above chance on the catch trials due to the challenging nature of
our procedure (see below). We also report data from \(N=\) 74 adult
participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
were tested but removed from analyses (again, using preregistered
exclusion criteria) because they had low scores on the catch trials or
because they were familiar with the non-English sound stimuli we used in
the adult experiment.

@@

{\centering \includegraphics{ms_blind_files/figure-latex/stim-1}

@@

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (about 800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing trial.

@@

{\centering \includegraphics{ms_blind_files/figure-latex/allData-1}

@@

\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}}
\vspace{1em}

@@

\clearpage

\renewcommand{\listfigurename}{Figure captions}

\listoffigures

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change explains discontinuities in word learning},
            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}

\authornote{ `The experiment, sample size, exclusion criteria,
and the model's main predictions were preregistered at
\url{https://osf.io/942gv/}'

`All data and analytic code are available at
\url{https://github.com/afourtassi/kidswitch}'

`None of the authors have any financial interest or a conflict of
interest regarding this work and this submission.'

@@

\begin{figure}[htbp]
\centering
\includegraphics{ms_full_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate
responses in the testing phase as a function of stimuli distinctiveness
\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
(For simplicity, we use model 2, which assumes that
\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
\end{figure}

@@

In this experiment, we tested participants in the word learning task
introduced above (Figure \ref{fig:task}). More precisely, we explored
the predictions related to both distinctiveness and precision. Sound
similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were
varied simultaneously in a within-subject design. Two age groups
(preschool children and adults) were tested on the same task\footnote{This
  four-condition within-subject design is relatively novel for
  preschoolers, but the tablet paradigm (Frank, Sugarman, Horowitz,
  Lewis, \& Yurovsky, 2016) allowed us to gather a relatively large
  number of trials from each child.} to explore whether development can
be characterized with the uncertainty parameters, \(\sigma_C\) and
\(\sigma_L\). The experiment, sample size, exclusion criteria, and the
model's main predictions were
pre-registered.\footnote{https://osf.io/942gv/}

@@

We report data from \(N=\) 63 children ages 4-5 years from the Bing
Nursery School on Stanford University's campus. An additional \(N=\) 39
children participated but were removed from analyses (using
preregistered exclusion criteria) because they were not above chance on
the catch trials due to the challenging nature of our procedure (see
below). We also report data from \(N=\) 74 adult participants tested on
Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed
from analyses (again, using preregistered exclusion criteria) because
they had low scores on the catch trials or because they were familiar
with the non-English sound stimuli we used in the adult experiment.

@@

{\centering \includegraphics{ms_full_files/figure-latex/stim-1}

@@

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (about 800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing
trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}

@@

{\centering \includegraphics{ms_full_files/figure-latex/allData-1}

@@

\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}}
\vspace{1em}

\section{Appendix}\label{appendix}

We show in Table 2 the output of the regression model we used to analyze
behavioral data in the experiment.

@@
